%%%% imav.tex
% This is the tex-file for the IMAV 2014 conference
% for questions / remarks / bugs regarding the files, please contact info@imavs.org
% You can use this style for your conference, as long as you refer to the IMAV 2014
% in a comment similar to this one.
% Of course, the IMAV 2014 is not liable for any aspects of its use.

\documentclass{article}
% The style file
\usepackage{imav}
% Use the postscript times font!
\usepackage{times}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{wasysym}
\usepackage{color}
%\numberwithin{algorithm}{chapter}
%\usepackage{algorithmicx}
% the following package is optional:
\usepackage{latexsym}

\usepackage [english]{babel}
\usepackage [autostyle, english = american]{csquotes}
\MakeOuterQuote{"}

\usepackage{acronym}


\title{Autonomous Flight of Micro Air Vehicles 2015 - Group 6}
\author{M. Bevernaegie\thanks{M.Bevernaegie@student.tudelft.nl}, C. Cheung\thanks{C.Cheung@student.tudelft.nl}, Y.I. Jenie\thanks{Y.I.Jenie-1@tudelft.nl}, S.H. Lee\thanks{S.H.Lee-2@student.tudelft.nl}, P. Lu\thanks{P.Lu-1@tudelft.nl} \\ Delft University of Technology, Delft, The Netherlands}

\begin{document}

\maketitle

\begin{abstract}
Before introducing the essential elements of successful vision-based obstacle avoidance the project and equipment are discussed. Using an AR Drone 2.0 and its HD front camera obstacles should be avoided in the TU Delft Cyber Zoo in a certain time frame without any human intervention; at the end of this quarter a competition will be done to see how well the drone will perform. The flight plan and airframe will be programmed beforehand using Paparazzi on a computer that is connected to the drone. Vision input and processing could be a demanding process for the drone and should be done efficiently. Literature on optic flow and computer vision methods is provided but should be adapted to fulfill the requirements of the project, i.e. image processing should be done wisely and iterations should be limited for the drone to react quickly. Next to the vision part, the case of flight plans with moving waypoints and fixed waypoints are discussed. Before the actual flight test was done a simulation program was developed in MATLAB for random obstacle placements and to test the vision algorithm. The actual flight in the competition showed satisfying results with no collisions and stable avoidance maneuvers but recommendations are given to optimize the avoidance system for the future.
\end{abstract}

\section{Introduction} \label{section:introduction}
\input{introduction}


\section{Vision algorithm}
\input{lit_vision}
\input{our_vision}

\section{Flight plan}
\input{Seong_fp}
\input{Peng_fp}
\input{fp_discussion}

\section{Simulation}
\label{section:simulation}
\input{Yazdi_sim}
\input{Seong_sim}

\section{Competition Result and Discussion}
\input{comp_results}
\section{Conclusion}
\input{conclusion}

% BIBLIOGRAPHY:
% use {unsrt}:
\bibliographystyle{unsrt}
\bibliography{imav_bibliography}

% The following lines are necessary for showing the appendices correctly, do not change!
\appendix
\newcommand{\appsection}[1]{\let\oldthesection\thesection
  \renewcommand{\thesection}{Appendix \oldthesection:}
  \section{#1}\let\thesection\oldthesection}
% appendices are now indicated by appsection:

\appsection{Data}
\appsection{More data}
\end{document}

